%%=========================================
\chapter{Recommendations for Future Work}\label{ch:further-work}
% You should give recommendations to possible extensions to your work. The recommendations should be as specific as possible, preferably with an objective and an indication of a possible approach.
%A further line of study based on concepts studied in this thesis would be a more in depth study of the 
%
%\mycomment{Skriv om ulike overflatebehandlinger, mulighet for å bruke nær-IR mikroskopi.}
% The recommendations may be classified as:
% • Short-term
% • Medium-term
% • Long-term
%%=========================================

%A possible extension of this work is
It would be useful to repeat the measurements on an additional (111)B-oriented substrate from vendor A to verify that the results from this study are reproducible, both in regards to the low density of particles on the as-received surface and the higher density after etch. The source of the grit particles that appeared on the surface after etch should be located by studying the bevelled edges and underneath the substrate, e.g. using \ac{sem} with \ac{eds}.

If the polishing grit observed on the etched surface of substrate A is revealed to originate from the substrate itself, ways to remove particles from the bevelled edges and underneath the substrate should be found. Possible methods could be rubbing a cleanroom swab soaked in solvent around the edges, mounting the substrate upside down to be able to remove particles from underneath, and try other standard semiconductor cleaning techniques \citep{reinhardt2008handbook}.

Then, different preparation etch procedures, i.e. shorter etch time or spray etching, should be examined. Seeing that \citet{benson2016analysis} reports that their \ce{Br}:methanol-based \ac{mbe} preparation etch removes residual \ce{SiO2} polishing grit from the substrates, a procedure that replicates their results should be developed.

A possible improvement of the preparation polish procedure could be to use both silica and alumina polishing grit during polishing. At the moment, alumina is used alone as the abrasive in the polishing procedure, but as both silica and alumina were present on the as-received substrates from vendor A, it could be assumed that a combination of these two is advantageous.

As a final test of the new preparation method, \ac{mct} films should be grown on one substrate prepared by the new method and one prepared by the old method. It would be interesting to compare the material properties and the quality of the resulting \ac{ir} detector element of the two films.

%\todo{EDX on another sub A as –received, check edges for grit particles, ways to remove these (different etch, use q-tip around edge? Shorter etch, perhaps spray etch EDX on stains – low voltage and perhaps tilt to get better surf sensitivity Same for sample with contrast matching transmission Final test: use modified sample prep procedure, then grow film and check properties (material and in the end component) Måle resistivitet på CZT forskjellige områder}


%Espen forslag:
%Benson reports lower grit densities after etch than in our work. We should try to replicate their results. It is unknown exactly how they rinse the substrate prior to etching.
%
%Some variations that could be tried are the following: 1) Rinsing the substrates in a spinner. Apply warm solvents and/or warm water onto the substrate. The liquid will then rush across the surface and hopefully remove surface particles. If the liquid is coupled to a megaultrasonic generator the cleaning efficiency will increase (Busnaina and Moumen, 2006). This method may be less effective to remove particles on the sides of the substrate which are not parallell to the substrate surface because the liquid will not flow across the sides. 2) Masking the surface and cleaning the edges of the sample with a q-tip dipped in solvent is another possibility.
% Busnaina, A.A. and Moumen, N., PostCMP Cleaning of ThermalOxide Wafers, Fabtech, 2006, 12th ed., pp. 293–297.

%Finne metode for å bli kvitt partikler fra kantene på vendor A substrat alik at de ikke løses opp i etsen og legger seg ned på substratoverflaten. Metode for å etse uten å legge igjen så mye partikler (1) ha en skillevegg i etsebegeret slik at en kan etse i det ene kammeret og så ta opp av væsken på andre siden av en glassvegg. Tendens til at partikler legger seg i overflaten, 2) noen løsemidler er bedre til å ta opp og vekk partikler enn andre.)

%Studere lav transmisjon og om det gir lysere områder i SEM og alltid eller bare der p-doping. Mørkere n-doping?

%Correlate the density of donuts with the density of tellurium precipitates near the surface.

% The future work section is a place for you to explain to your readers where you think the results can lead you. What do you think are the next steps to take? What other questions do your results raise? Do you think certain paths seem to be more promising than others?
% The goal should not be to go into a bunch of details, but instead just a sentence or two explaining each idea.

%%=========================================